Differential invariant signatures for planar Lie group transformations of images

### 2020-08-26 paper/newpaper.tex
Some additions, not enough

@@

\subsection{Transformation notation}
Most of the time we will work on grey-scale transformations of two-dimensional images. In this setting, we define the transformation group action by a coordinate transformation $\varphi \colon \mathbb{R}^2 \to \mathbb{R}^2$
\begin{equation}\label{eq:transformation}
  \mathbf{x} \mapsto \bar{\mathbf{x}} = \varphi(\mathbf{x})
\end{equation}
The transformed image is then defined to be
\begin{equation}\label{eq:fbarequalsf}
  \bar{f}(\bar{\mathbf{x}}) = (f\circ\varphi^{-1})(\bar{\mathbf{x}}) = f(\mathbf{x}).
\end{equation}
Derivatives of $\bar{f}$ and $f$ can be related by the chain rule, for example the first order derivatives are given by:
\begin{equation}\label{eq:prolongation}
  \begin{aligned}
    f_x &= \bar{f}_{\bar{x}} \bar{x}_x + \bar{f}_{\bar{y}}\bar{y}_x \\
    f_y &= \bar{f}_{\bar{x}} \bar{x}_y + \bar{f}_{\bar{y}}\bar{y}_y \\
  \end{aligned}
\end{equation}
where $\bar{x}_x = \frac{\partial \varphi_1}{\partial x}(x, y)$, et cetera. It is often convenient to work with $\varphi^{-1}$ instead, which we will do in \S\ref{sec:movingframes}.

@@

@@

SE(2) is done via the moving frame by Olver in Ch 8 of CIT.

\section{Differential invariants of E(2) through tensor contraction}
While we avoid the use of tensors in most of this study, there is a notable exception to be made for the Euclidean transformation group $E(2)$. In this setting we can restrict ourselves to \emph{Cartesian tensors}, where we need make no distinction between covariance and contravariance, they are both the same thing. We use subscript indices exclusively, for this reason.

@@

With respect to $\mathbb{R}^2$, a Cartesian tensor of rank $p$, or $p$-tensor is a $2^p$-tuple of real numbers $C_{i_1\ldots i_p}$ whose components transform under a Euclidean transformation as
\begin{equation*}
  \bar{C}_{i_1\ldots i_p} = a_{i_1j_1}\cdots a_{i_pj_p} C_{j_1\ldots j_p}
\end{equation*}
and a $0$-tensor is a scalar, or invariant.

@@

\todo[inline]{Expand to Sim(2)}
\todo[inline]{Introduce image that we are going to use in subsequenct examples}
\todo[inline]{Introduce signatures - 3D and 4D perhaps?}

@@

For example, consider a weight $2$ transvectant defined as
\begin{align*}
    \mbox{tr} &\left[(\Omega_{12}\Omega_{12}) f(x_1, y_1)f(x_2, y_2)\right] \\
    &= \mbox{tr}\left[(\partial_{x_1 y_2} - \partial_{x_2y_1})(\partial_{x_1 y_2} -
    \partial_{x_2y_1})f(x_1, y_1)f(x_2, y_2)\right]\\
    &= \mbox{tr}\left[\left(\partial_{x_1 y_2} - \partial_{x_2 y_1}\right)\left(f_x(x_1, y_1)f_y(x_2, y_2) - f_y(x_1, y_1)f_x(x_2, y_2)\right)\right] \\
    &= \mbox{tr}\left[f_{xx}(x_1, y_1)f_{yy}(x_2, y_2) - f_{xy}(x_1, y_1)f_{xy}(x_2, y_2)\right] \\
    &= f_{xx}(x, y) f_{yy}(x, y) - f_{xy}(x, y)^2
\end{align*}
This is a degree $2$ partial transvectant as it involves derivatives of $f$
up to second order, and can be represented graphically by the following
diagram,
\begin{center}
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
    \draw[-] (1) to [out=30,in=150] (2);
    \draw[-] (1) to [out=-30,in=-150] (2);
\end{tikzpicture}
\end{center}
where the double edge between nodes $1$ and $2$ corresponds to the two copies of $\Omega_{12}$.
Tables~\ref{tab:transvectants1} and~\ref{tab:transvectants2} shows all possible nonzero partial
transvectants of $A_2$ up to weight $4$ that can be generated in this way.
Note that the weight is the number of edges in the graph.
\begin{table}
\centering
\begin{tabular}{cccp{11cm}}
Degree & Weight & Diagram & Partial transvectant\\
\hline
2 & 2 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
    \draw[-] (1) to [out=30,in=150] (2);
    \draw[-] (1) to [out=-30,in=-150] (2);
\end{tikzpicture}
& $2 f_{xx} f_{yy} - 2 \left(f_{xy}\right)^{2}$ \\

@@

@@

% =========
2 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
    \draw[-] (1) to (2);
    \draw[-] (2) to (3);
    \draw[-] (3) to (4);
    \draw[-] (4) to (5);
\end{tikzpicture}
& $\left(f_{x}\right)^{2} f_{xx} \left(f_{yy}\right)^{2} - \left(f_{x}\right)^{2} f_{yy} \left(f_{xy}\right)^{2} - 2 f_{x} f_{xx} f_{y} f_{yy} f_{xy} + 2 f_{x} f_{y} \left(f_{xy}\right)^{3} + \left(f_{xx}\right)^{2} \left(f_{y}\right)^{2} f_{yy} - f_{xx} \left(f_{y}\right)^{2} \left(f_{xy}\right)^{2}$ \\

3 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
    \draw[-] (1) to (4);
    \draw[-] (4) to (5);
\end{tikzpicture}
& $- \left(f_{x}\right)^{3} f_{yy} f_{xyy} + \left(f_{x}\right)^{3} f_{yyy} f_{xy} - \left(f_{x}\right)^{2} f_{xx} f_{y} f_{yyy} + 2 \left(f_{x}\right)^{2} f_{y} f_{yy} f_{xxy} - \left(f_{x}\right)^{2} f_{y} f_{xy} f_{xyy} + 2 f_{x} f_{xx} \left(f_{y}\right)^{2} f_{xyy} - f_{x} f_{xxx} \left(f_{y}\right)^{2} f_{yy} - f_{x} \left(f_{y}\right)^{2} f_{xy} f_{xxy} - f_{xx} \left(f_{y}\right)^{3} f_{xxy} + f_{xxx} \left(f_{y}\right)^{3} f_{xy}$ \\
\end{tabular}
\caption{Details and graphical representations of all partial transvectants up to degree $3$ of copies of a function $f$ under a transformation in $A(2)$.}
\label{tab:transvectants1}
\end{table}

\begin{table}
\centering
\begin{tabular}{cccp{11cm}}
Degree & Weight & Diagram & Partial transvectant\\
\hline
4 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
    \draw[-] (1) to (4);
    \draw[-] (1) to (5);
\end{tikzpicture}
& $\left(f_{x}\right)^{4} f_{yyyy} - 4 \left(f_{x}\right)^{3} f_{y} f_{xyyy} + 6 \left(f_{x}\right)^{2} \left(f_{y}\right)^{2} f_{xxyy} - 4 f_{x} \left(f_{y}\right)^{3} f_{xxxy} + f_{xxxx} \left(f_{y}\right)^{4}$ \\

4 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
    \draw[-] (1) to [out=30,in=150] (2);
    \draw[-] (1) to [out=-30,in=-150] (2);
    \draw[-] (1) to [out=10,in=170] (2);
    \draw[-] (1) to [out=-10,in=-170] (2);
\end{tikzpicture}
& $f_{xxxx} f_{yyyy} - 4 f_{xyyy} f_{xxxy} + 3 f_{xxyy}^2$ \\

@@

4 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
    \draw[-] (1) to [out=-150,in=90] (2);
    \draw[-] (1) to [out=-90,in=30] (2);
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
\end{tikzpicture} 
& $ f_{x} f_{xxx} f_{yyyy} - f_x f_{yyy} f_{xxxy} + 3 f_{x} f_{xyy} f_{xxyy} - 3 f_x f_{xyyy} f_{xxy} - f_{xxx} f_y f_{xyyy} + f_{xxxx} f_y f_{yyy} - 3 f_y f_{xyy} f_{xxxy} + 3 f_y f_{xxy} f_{xxyy}$ \\
\end{tabular}
\caption{Details and graphical representations of all partial transvectants of weight $4$ of copies of a function $f$ under a transformation in $A(2)$.}
\label{tab:transvectants2}
\end{table}

@@

Hence, we can form a signature for $SA(2)$ by choosing any combination of
partial transvectants. We'll choose a signature with three components so that
it can be visualised as a three-dimensional surface; note that this will not
be complete and may well have a \emph{very large bad set}. For example, we can choose the function value together with the first two partial transvectants to form the signature
\begin{equation*}
    \left(f, f_{xx}f_{yy}-f_{xy}^2, f_x^2f_{yy} - 2f_xf_yf_{xy} + f_{xx}f_y^2\right)
\end{equation*}

\subsubsection{Example}
Consider as our image, the function $f(x, y) = 0.5 - 0.2x - 0.3y - 0.05x^2 +
0.03xy + 0.04y^2 + 0.03y^3 +0.001x^3 - 0.0015x^2y + 0.002xy^2 - 0.0005y^3$
defined on $[0, 1]\times[0, 1]$.
\todo[inline]{remake figure with modified matrix. Also modify function so it has some features like a critical point}
We'll subject our image to a special affine transformation:
\begin{equation*}
\mathbf{x} \mapsto \frac{1}{1.1}\begin{bmatrix} 0.6875 & 1.1 \\ -0.6 & 0.8 \end{bmatrix}\mathbf{x} + \begin{bmatrix} 0.1 \\ -0.2 \end{bmatrix}
\end{equation*}
Fig.~\ref{fig:SA2} shows the function as a greyscale image, the transformed
function, and the signatures of both the untransformed and transformed
images.
\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/f_transformed_SA2.png}
\includegraphics[width=.45\textwidth]{Figs/SA2_signature.png}
\caption{\todo[inline]{add extra crap} A sample $SA(2)$ Transform and 3D signature. Mention what's going on with the grid.}
\label{fig:SA2}
\end{figure}

@@

@@

Identifying $\R^2$ with $\mathbb{C}$, the M\"obius group is a real 6-dimensional local Lie group acting on $\mathbb{R}^2$.
It is the smallest nonlinear planar group that contains $SE(2)$, and it is the set of biholomorphic maps of the Riemann sphere; it also has direct applications in image processing since it arises in the {\em conformal camera} model of vision, in which scenes are projected radially onto a sphere \cite{lenz1990group,turski2004geometric}. 
%Different shapes may be related by M\"obius transformations, as is explored by Petukhov \cite{petukhov1989non} for biological objects: in one example, the human skull grows approximately by M\"obius transformations.  Note also that Thompson \cite{thompson1942growth} famously deformed images of one species to match those of another, many of his examples using conformal mappings, and thus may be approximated (or even determined by) M\"obius transformations. Discussing this work, Milnor \cite{milnor2010growth}  argued that ``The geometrically simplest way to change the relative size of different body parts would be by a conformal transformation. It seems plausible that this simplest solution will often be the most efficient, so that natural selection tend to choose it.'' (Milnor was thinking of 3D conformal transformations, whose restriction to 2D is the M\"obius transformations.)

The 0th order moving frame translates $z$ to $\beta$. We can therefore take $\beta=0$; we are also free to take $\delta=1$. This leaves 4 group parameters $a,b,c,d$, where $\alpha = a + i b$, $\gamma = c + i d$, to be determined as follows. First we prolong the action to 3rd derivatives of $f$. There are 9 derivatives of $f$ of order 1, 2, and 3, so there must be at least 5 invariants.
\todo[inline]{General thm for this earlier...}

The prolonged action is:
\begin{equation}
\arraycolsep=1.4pt
\left(
\begin{array}{c}
  \bar f_x \\ \bar f_y \\ \bar f_{xx} \\ \bar f_{xy} \\ \bar f_{yy} \\ \bar f_{xxx} \\ \bar f_{xxy} \\ \bar f_{xyy} \\ \bar f_{yyy} 
 \end{array}
 \right)
 = 
\left(
\begin{array}{ccccccccc}
 a & b & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
 -b & a & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
 2\mu & -2 \rho & a^2 & 2 a b & b^2 & 0 & 0 & 0 & 0 \\
 2 \rho & 2\mu & -a b & a^2\!-b^2 & a b & 0 & 0 & 0 & 0 \\
 -2\mu & 2 \rho & b^2 & -2 a b & a^2 & 0 & 0 & 0 & 0 \\
 -6 (2 b c d+a \lambda) & 6 (2 a c d-b\lambda) & 6 a \mu &
  M_{64}  & -6 b \rho & a^3 & 3 a^2 b & 3 a b^2 & b^3 \\
 -6 (2 a c d-b\lambda) & -6 (2 b c d+a \lambda) & M_{73}& M_{74} & 
 M_{75} & -a^2 b & a^3\!-2 a b^2 & 2
   a^2 b\!-b^3 & a b^2 \\
 6 (2 b c d+a \lambda) & -6 (2 a c d-b\lambda) & M_{83} & M_{84} & M_{85} & a b^2 & b^3\!-2
   a^2 b & a^3\!-2 a b^2 & a^2 b \\
 6 (2 a c d-b\lambda) & 6 (2 b c d+a \lambda) & 6 b \mu & 
  M_{94} & 6 a \rho & -b^3 & 3 a b^2 & -3 a^2 b & a^3 \\
\end{array}
\right)\left(
\begin{array}{c}
f_x \\ f_y \\ f_{xx} \\ f_{xy} \\ f_{yy} \\ f_{xxx} \\ f_{xxy} \\ f_{xyy} \\ f_{yyy} 
 \end{array}
 \right).
\label{eqn:mobius}
 \end{equation}
 where
 \begin{equation*}
 \begin{array}{lll}
M_{64}=-12abc+6d(a^2-b^2), & 
M_{73}=4 d a^2+6 b c a-2 b^2 d, & 
M_{74}=-6 c a^2+12 b d a+6 b^2 c, \\
 M_{75}=-2 d a^2-6 b c a+4 b^2 d, &
 M_{83}=2 c a^2-6 b d a-4 b^2 c, &
 M_{84}=6 (d a^2+2 b c a-b^2 d),\\
 M_{85}=-4 c a^2+6 b d a+2 b^2 c,& 
 M_{94}= -12a b d + 6c(a^2-b^2),\\
\lambda=d^2-c^2, & 
\mu = b d - a c, & 
\rho = b c + a d.
\end{array}
\end{equation*}

>>>>

Some examples, plus mention Kendall shape.

@@

\subsection{Transformation notation}
Most of the time we will work on grey-scale transformations of two-dimensional images. In this setting, we define the transformation group action by a coordinate transformation $\varphi \colon \mathbb{R}^2 \to \mathbb{R}^2$:
\begin{equation}\label{eq:transformation}
  \mathbf{x} \mapsto \bar{\mathbf{x}} = \varphi(\mathbf{x})
\end{equation}
The transformed image is then defined to be:
\begin{equation}\label{eq:fbarequalsf}
  \bar{f}(\bar{\mathbf{x}}) = (f\circ\varphi^{-1})(\bar{\mathbf{x}}) = f(\mathbf{x}).
\end{equation}
Derivatives of $\bar{f}$ and $f$ can be related by the chain rule, for example the first order derivatives are given by:
\begin{equation}\label{eq:prolongation}
  \begin{aligned}
    f_x &= \bar{f}_{\bar{x}} \bar{x}_x + \bar{f}_{\bar{y}}\bar{y}_x \\
    f_y &= \bar{f}_{\bar{x}} \bar{x}_y + \bar{f}_{\bar{y}}\bar{y}_y \\
  \end{aligned}
\end{equation}
where $\bar{x}_x = \frac{\partial \varphi_1}{\partial x}(x, y)$, et cetera. It is often convenient to work with $\varphi^{-1}$ instead, as in \S\ref{sec:movingframes}.

Mention colour here.

@@

Signatures

Idea, some notation, then completeness, bad set, have not removed the recognition problem, just removed the group variation.

---
TEXT FROM OUR MOBIUS PAPER
Calabi et al. [9] propose the use of differential invariant signatures for shape analysis, and further
argue that these should be approximated in a group-invariant way. For example, for the Euclidean
group, the signature is the shape (; s) regarded as a subset of R2. The claimed advantages
of the approach are that the signature determines the shape; that it does not depend on the
choice of initial point on the curve or on parameterization by arclength, and that its G-invariance
makes it robust; and that it is based on a general procedure for arbitrary objects and groups.
See [2, 4, 9, 18, 30, 35, 36] for further developments and applications of the invariant signature.
Although the signature at first sight appears to be complete (e.g., Theorem 5.2 in [9]),
a more detailed treatment (e.g., [17, 28]) highlights the fact that it is not complete on shapes
that contain singular parts { straight and circular segments in the Euclidean case. For these
parts, the signature reduces to a point. Thus, for shapes that have nearly straight or nearly
circular segments, the signature cannot be robust. In addition, while the signature does not
depend on the starting point or the parameterization, it takes values in a very complicated set,
namely, the planar shapes. To compare the invariants of two shapes requires comparing two
shapes. Essentially, the parameterization-dependence has only been deferred to a later stage
of the analysis (unless one is content to compare shapes visually). One approach to this is to
weight the signature, see [32] for more details.
---

@@

\section{Differential invariants of $E(2)$ through tensor contraction}
While we avoid the use of tensors in most of this study, there is a notable exception to be made for the Euclidean transformation group $E(2)$. In this setting we can restrict ourselves to \emph{Cartesian tensors}, where we need make no distinction between covariance and contravariance, as they are equivalent; we therefore use subscript indices exclusively.

@@

With respect to $\mathbb{R}^2$, a Cartesian tensor of rank $p$, or $p$-tensor is a $2^p$-tuple of real numbers $C_{i_1\ldots i_p}$ whose components transform under a Euclidean transformation as:
\begin{equation*}
  \bar{C}_{i_1\ldots i_p} = a_{i_1j_1}\cdots a_{i_pj_p} C_{j_1\ldots j_p}
\end{equation*}
and a $0$-tensor is a scalar, or invariant.

@@

\todo[inline]{Expand to Sim(2)}
\todo[inline]{Introduce image that we are going to use in subsequent examples}
\todo[inline]{Introduce signatures - 3D and 4D perhaps?}

@@

For example, consider a weight $2$ transvectant defined as
\begin{align*}
    \mbox{tr} &\left[(\Omega_{12}\Omega_{12}) f(x_1, y_1)f(x_2, y_2)\right] \\
    &= \mbox{tr}\left[(\partial_{x_1 y_2} - \partial_{x_2y_1})(\partial_{x_1 y_2} -
    \partial_{x_2y_1})f(x_1, y_1)f(x_2, y_2)\right]\\
    &= \mbox{tr}\left[\left(\partial_{x_1 y_2} - \partial_{x_2 y_1}\right)\left(f_x(x_1, y_1)f_y(x_2, y_2) - f_y(x_1, y_1)f_x(x_2, y_2)\right)\right] \\
    &= \mbox{tr}\left[f_{xx}(x_1, y_1)f_{yy}(x_2, y_2) - f_{xy}(x_1, y_1)f_{xy}(x_2, y_2)\right] \\
    &= f_{xx}(x, y) f_{yy}(x, y) - f_{xy}(x, y)^2
\end{align*}
This is a degree $2$ partial transvectant as it involves derivatives of $f$
up to second order, and can be represented graphically by the following
diagram,
\begin{center}
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
    \draw[-] (1) to [out=30,in=150] (2);
    \draw[-] (1) to [out=-30,in=-150] (2);
\end{tikzpicture}
\end{center}
where the double edge between nodes $1$ and $2$ corresponds to the two copies of $\Omega_{12}$.
Tables~\ref{tab:transvectants1} and~\ref{tab:transvectants2} shows all possible nonzero partial
transvectants of $A_2$ up to weight $4$ that can be generated in this way.
Note that the weight is the number of edges in the graph.

\begin{table}
\centering
\begin{tabular}{cccp{11cm}}
Degree & Weight & Diagram & Partial transvectant\\
\hline
2 & 2 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
    \draw[-] (1) to [out=30,in=150] (2);
    \draw[-] (1) to [out=-30,in=-150] (2);
\end{tikzpicture}
& $2 f_{xx} f_{yy} - 2 \left(f_{xy}\right)^{2}$ \\

@@

2 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
    \draw[-] (1) to (2);
    \draw[-] (2) to (3);
    \draw[-] (3) to (4);
    \draw[-] (4) to (5);
\end{tikzpicture}
& $\left(f_{x}\right)^{2} f_{xx} \left(f_{yy}\right)^{2} - \left(f_{x}\right)^{2} f_{yy} \left(f_{xy}\right)^{2} - 2 f_{x} f_{xx} f_{y} f_{yy} f_{xy} + 2 f_{x} f_{y} \left(f_{xy}\right)^{3} + \left(f_{xx}\right)^{2} \left(f_{y}\right)^{2} f_{yy} - f_{xx} \left(f_{y}\right)^{2} \left(f_{xy}\right)^{2}$ \\

@@

% =========
3 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
    \draw[-] (1) to (4);
    \draw[-] (4) to (5);
\end{tikzpicture}
& $- \left(f_{x}\right)^{3} f_{yy} f_{xyy} + \left(f_{x}\right)^{3} f_{yyy} f_{xy} - \left(f_{x}\right)^{2} f_{xx} f_{y} f_{yyy} + 2 \left(f_{x}\right)^{2} f_{y} f_{yy} f_{xxy} - \left(f_{x}\right)^{2} f_{y} f_{xy} f_{xyy} + 2 f_{x} f_{xx} \left(f_{y}\right)^{2} f_{xyy} - f_{x} f_{xxx} \left(f_{y}\right)^{2} f_{yy} - f_{x} \left(f_{y}\right)^{2} f_{xy} f_{xxy} - f_{xx} \left(f_{y}\right)^{3} f_{xxy} + f_{xxx} \left(f_{y}\right)^{3} f_{xy}$ \\
\end{tabular}
\caption{Details and graphical representations of all partial transvectants up to degree $3$ of copies of a function $f$ under a transformation in $A(2)$.}
\label{tab:transvectants1}
\end{table}

\begin{table}
\centering
\begin{tabular}{cccp{11cm}}
Degree & Weight & Diagram & Partial transvectant\\
\hline
4 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
    \draw[-] (1) to [out=30,in=150] (2);
    \draw[-] (1) to [out=-30,in=-150] (2);
    \draw[-] (1) to [out=10,in=170] (2);
    \draw[-] (1) to [out=-10,in=-170] (2);
\end{tikzpicture}
& $f_{xxxx} f_{yyyy} - 4 f_{xyyy} f_{xxxy} + 3 f_{xxyy}^2$ \\

@@

4 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,0.866) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.5,0) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (0.5,0) {3};
    \draw[-] (1) to [out=-150,in=90] (2);
    \draw[-] (1) to [out=-90,in=30] (2);
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
\end{tikzpicture} 
& $ f_{x} f_{xxx} f_{yyyy} - f_x f_{yyy} f_{xxxy} + 3 f_{x} f_{xyy} f_{xxyy} - 3 f_x f_{xyyy} f_{xxy} - f_{xxx} f_y f_{xyyy} + f_{xxxx} f_y f_{yyy} - 3 f_y f_{xyy} f_{xxxy} + 3 f_y f_{xxy} f_{xxyy}$ \\

4 & 4 &
\begin{tikzpicture}[baseline=0]
    \node[draw,circle,minimum size=0.2cm] (1) at (0,1) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (-0.9511,0.3090) {2};
    \node[draw,circle,minimum size=0.2cm] (3) at (-0.5878,-.8090) {3};
    \node[draw,circle,minimum size=0.2cm] (4) at (0.5878,-.8090) {4};
    \node[draw,circle,minimum size=0.2cm] (5) at (0.9511,0.3090) {5};
    \draw[-] (1) to (2);
    \draw[-] (1) to (3);
    \draw[-] (1) to (4);
    \draw[-] (1) to (5);
\end{tikzpicture}
& $\left(f_{x}\right)^{4} f_{yyyy} - 4 \left(f_{x}\right)^{3} f_{y} f_{xyyy} + 6 \left(f_{x}\right)^{2} \left(f_{y}\right)^{2} f_{xxyy} - 4 f_{x} \left(f_{y}\right)^{3} f_{xxxy} + f_{xxxx} \left(f_{y}\right)^{4}$ \\
\end{tabular}
\caption{Details and graphical representations of all partial transvectants of weight $4$ of copies of a function $f$ under a transformation in $A(2)$.}
\label{tab:transvectants2}
\end{table}

@@

Hence, we can form a signature for $SA(2)$ by choosing any combination of
partial transvectants. We'll choose a signature with three components so that
it can be visualised as a three-dimensional surface; note that this will not
be complete and may well have a very large bad set. For example, we can choose the function value together with the first two partial transvectants to form the signature:
\begin{equation*}
    \left(f, f_{xx}f_{yy}-f_{xy}^2, f_x^2f_{yy} - 2f_xf_yf_{xy} + f_{xx}f_y^2\right)
\end{equation*}

\subsubsection{Example}
Consider as our image, the function $f(x, y) = 0.5 - 0.2x - 0.3y - 0.05x^2 +
0.03xy + 0.04y^2 + 0.03y^3 +0.001x^3 - 0.0015x^2y + 0.002xy^2 - 0.0005y^3$
defined on $[0, 1]\times[0, 1]$.
\todo[inline]{remake figure with modified matrix. Also modify function so it has some features like a critical point}
We'll subject our image to a special affine transformation:
\begin{equation*}
\mathbf{x} \mapsto \frac{1}{1.1}\begin{bmatrix} 0.6875 & 1.1 \\ -0.6 & 0.8 \end{bmatrix}\mathbf{x} + \begin{bmatrix} 0.1 \\ -0.2 \end{bmatrix}
\end{equation*}

Fig.~\ref{fig:SA2} shows the function as a greyscale image, the transformed
function, and the signatures of both the untransformed and transformed
images.
\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/f_transformed_SA2.png}
\includegraphics[width=.45\textwidth]{Figs/SA2_signature.png}
\caption{\todo[inline]{add extra crap} A sample $SA(2)$ Transform and 3D signature. Mention what's going on with the grid.}
\label{fig:SA2}
\end{figure}

@@

Idea is that it is the transformation back to the cross-section.

@@

Identifying $\R^2$ with $\mathbb{C}$, the M\"obius group is a real 6-dimensional local Lie group acting on $\mathbb{R}^2$.
It is the smallest nonlinear planar group that contains $SE(2)$, and it also has direct applications in image processing since it arises in the {\em conformal camera} model of vision, in which scenes are projected radially onto a sphere \cite{lenz1990group,turski2004geometric}; it is also the set of biholomorphic maps of the Riemann sphere. 
%Different shapes may be related by M\"obius transformations, as is explored by Petukhov \cite{petukhov1989non} for biological objects: in one example, the human skull grows approximately by M\"obius transformations.  Note also that Thompson \cite{thompson1942growth} famously deformed images of one species to match those of another, many of his examples using conformal mappings, and thus may be approximated (or even determined by) M\"obius transformations. Discussing this work, Milnor \cite{milnor2010growth}  argued that ``The geometrically simplest way to change the relative size of different body parts would be by a conformal transformation. It seems plausible that this simplest solution will often be the most efficient, so that natural selection tend to choose it.'' (Milnor was thinking of 3D conformal transformations, whose restriction to 2D is the M\"obius transformations.)

We are free to take $\delta=1$. Then $\bar f = f$ means that $z$ is translated to $\beta$; we can therefore take $\beta=0$. This leaves 4 group parameters $a,b,c,d$, where $\alpha = a + i b$, $\gamma = c + i d$, to be determined as follows. We prolong the action to 2nd derivatives of $f$, which is sufficient to allow the group to act freely. There are 5 derivatives of $f$ up to order 2, so there will be at least 1 invariant. In order to find further invariants the prolongation to 3rd derivatives is required, which will result in at least another four invariants. %There are 9 derivatives of $f$ of order 1, 2, and 3, so there must be at least 5 invariants.
\todo[inline]{General thm for this earlier...}

The prolonged action is:
\begin{equation}
\arraycolsep=1.4pt
\left[
\begin{array}{c}
  \bar f_x \\ \bar f_y \\ \bar f_{xx} \\ \bar f_{xy} \\ \bar f_{yy} 
 \end{array}
 \right]
 = 
\left[
\begin{array}{ccccc}
 a & b & 0 & 0 & 0 \\
 -b & a & 0 & 0 & 0 \\
 2\mu & -2 \rho & a^2 & 2 a b & b^2 \\
 2 \rho & 2\mu & -a b & a^2\!-b^2 & a b \\
 -2\mu & 2 \rho & b^2 & -2 a b & a^2 \\
\end{array}
\right]\left[
\begin{array}{c}
f_x \\ f_y \\ f_{xx} \\ f_{xy} \\ f_{yy} \\
 \end{array}
 \right].
\label{eqn:mobius}
 \end{equation}

\noindent where $\mu = b d - a c$ and $\rho = b c + a d$.
